Cats and Dogs Recognition

### 2013-12-06 paper.tex
w

\section{Introduction}
The Asirra CAPTCHA [7], proposed at ACM CCS 2007, relies on the problem of distinguishing images of cats and dogs (Asirra short for Animal Species Image Recognition for Restricting Access"). An Asirra challenge consists of 12 images, each of which is of either a cat or a dog. To solve the CAPTCHA, the user must select all the cat images, and none of the dog images. This is a task that humans are very good at. According to [7], Asirra can be solved by humans 99.6$\%$ of the time in under 30 seconds. The usability of Asirra is a significant advantage compared to text recognition based CAPTCHAs. The preference towards Asirra is due to the presumed difficulty of classifying images of cats and dogs solely by machine (evidence given by [7]). A classifier based on color features, described in [7], is only 56.9$\%$ accurate. Golle [1] suggests classification accuracy of better than 60$\%$ will be difficult without a significant advance in the state of the art". However, with a 60$\%$ accurate classifier, the probability of solving a 12-image Asirra challenge is roughly 0.2$\%$.

\section{Related Work}
 [1] proposes a classifier which is 82.7$\%$ accurate in telling part images of cats and dogs, which yields 10.3$\%$ odds in passing the 12-image Asirra task. Their choice of features are elegant yet straightforward, namely color and texture. The colors are interpreted in the hue-saturation-value (hsv) model, which is close to how people perceive colors. The other choice are red-green-blue (rgb), hue-saturation-light (hsl), and hue-saturation-intensity (hsi) models. We expect the choice of different models will generally affect the classifying results to some degree. Their color feature records the existence of a pixel with in some particular color region ($h,s,v$) in a cell. We adopt the same approach and try some variant models. Their texture feature, using the structural approach (will be explained in the texture feature section), mainly describe the variance of the colors of the image in the rob space. They achieve an accuracy of 82.7$\%$ by combining the SVM results of the two kinds of features with 8000 training examples on 2000 testing samples. However, we believe using other perspectives, in our case gradient features, of the image instead of rgb-cast colors will improve the classification. Our first texture features follow statistical approach with similar underlying philosophy as []'s. We use the naive statistics ???????? offset energy (difference in means of the regions), entropy (difference in variances of the regions) blabla. The result is slightly worse than []. Considering the naivete and crudeness of the texture model, we anticipate a considerable ascendancy over []'s by refining our texture model. Improvement can be made by using more complicated features characterizing the texture, say the well known Histogram of Oriented Gradient (HOG), and BLP (binary local patterns). We do some test cases with training sample size ?? and testing sample size ??. The result is significantly better than [] with small sample sizes (xiangcy give example!!!!). There are three options. The first is to extract HOG, BLP of the whole image to run boosting, select a subset of most distinguishing features, and apply SVM. The second and third options ??? body and face??. The third option does a similar task as face detection. However, as commented in Zhang, Sun, and Tang [], applying the existing face detection approaches to detect the cat head is not feasible not only due to apparent greater appearance variations of cat faces compared to those of human faces, but also due to their more complicated textures. Same for dog faces. So it requires a different detection strategy. We tried the approaches in their paper. They used Haar of Histogram of Gradients as feature vector to train a detector for cat heads. The positive face examples are manually labeled out eyes and ears and normalized by aligning ears or eyes. However, normalizing the dog faces is much harder than cats because of larger variety of dog faces. Moreover, we are dealing with database with more diversity in face positions and directions. In particular, we took an approach mimicking the cascade ideas of Viola Jones $\cite{viola}$. Increasing layers has an considerable effect on reducing test errors -- in $\cite{viola}$, Viola and Jones trained a 37 layer decision tree to achieve over 85 percent performance, using thousands of positive examples and millions of negative examples. Due to limitation of time and machines, we use a decision tree of roughly 10 layers. Once we crop out heads from the original images, we use boost algorithm to train a classifier to classify cat heads and dog heads. This classifier will be much more accurate than classifiers directly trained from the whole image. In this part, we use HOOGs as our feature vectors. By training 200 cat heads and 200 dog heads, we get a classifier with performance higher than $90\%$.

@@

\begin{thebibliography}{99}
\bibitem{viola} 
\bibitem{sun} 
\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
The Asirra CAPTCHA $\cite{golle}$, proposed at ACM CCS 2007, relies on the problem of distinguishing images of cats and dogs (Asirra short for Animal Species Image Recognition for Restricting Access"). An Asirra challenge consists of 12 images, each of which is of either a cat or a dog. To solve the CAPTCHA, the user must select all the cat images, and none of the dog images. This is a task that humans are very good at. According to $\cite{golle}$, Asirra can be solved by humans 99.6$\%$ of the time in under 30 seconds. The usability of Asirra is a significant advantage compared to text recognition based CAPTCHAs. The preference towards Asirra is due to the presumed difficulty of classifying images of cats and dogs solely by machine. A classifier based on color features, described in $\cite{asirra}$, is only 56.9$\%$ accurate. $\cite{asirra}$ suggests classification accuracy of better than 60$\%$ will be difficult without a significant advance in the state of the art". However, with a 60$\%$ accurate classifier, the probability of solving a 12-image Asirra challenge is roughly 0.2$\%$. Later work on the field, for example $\cite{golle}$, has improved the specification of the feature vectors, which highly increases the probability of correctly classifying a single cat or dog image. In our work, we employ techniques, for example cascade procedure and image integral in $\cite{viola}$, from more general object detection settings, and combine them with promising feature vectors in the relevant research topics, in particular, HOG like features. We try different combination of color features and texture features to obtain a much better classifier under small training sample compared with those in $\cite{golle}$.

\section{Related Work}
$\cite{golle}$ proposes a classifier which is 82.7$\%$ accurate in telling part images of cats and dogs, which yields 10.3$\%$ odds in passing the 12-image Asirra task. Their choice of features are elegant yet straightforward, namely color and texture. The colors are interpreted in the hue-saturation-value (hsv) model, which is close to how people perceive colors. The other choice are red-green-blue (rgb), hue-saturation-light (hsl), and hue-saturation-intensity (hsi) models. We expect the choice of different models will generally affect the classifying results to some degree. Their color feature records the existence of a pixel with in some particular color region ($h,s,v$) in a cell. We adopt the same approach and try some variant models. Their texture feature, using the structural approach (will be explained in the texture feature section), mainly describe the variance of the colors of the image in the rob space. They achieve an accuracy of 82.7$\%$ by combining the SVM results of the two kinds of features with 8000 training examples on 2000 testing samples. However, we believe using other perspectives, in our case gradient features, of the image instead of rgb-cast colors will improve the classification. Our first texture features follow the statistical approach with similar underlying philosophy as $\cite{viola}$'s. We use the naive statistics, energy, contrast, correlation, and homogeneity (see section 3). The result is slightly worse than $\cite{goole}$. Considering the naivete and crudeness of the texture model, we anticipate a considerable ascendancy over []'s by refining our texture model. Improvement can be made by using more complicated features characterizing the texture, say the well known Histogram of Oriented Gradient (HOG), and BLP (binary local patterns). We do some test cases with training sample size ?? and testing sample size ??. The result is significantly better than [] with small sample sizes (xiangcy give example!!!!). There are three options. The first is to extract HOG, BLP of the whole image to run boosting, select a subset of most distinguishing features, and apply SVM. The second and third options ??? body and face??. The third option does a similar task as face detection. However, as commented in Zhang, Sun, and Tang [], applying the existing face detection approaches to detect the cat head is not feasible not only due to apparent greater appearance variations of cat faces compared to those of human faces, but also due to their more complicated textures. Same for dog faces. So it requires a different detection strategy. We tried the approaches in their paper. They used Haar of Histogram of Gradients as feature vector to train a detector for cat heads. The positive face examples are manually labeled out eyes and ears and normalized by aligning ears or eyes. However, normalizing the dog faces is much harder than cats because of larger variety of dog faces. Moreover, we are dealing with database with more diversity in face positions and directions. In particular, we took an approach mimicking the cascade ideas of Viola Jones $\cite{viola}$. Increasing layers has an considerable effect on reducing test errors -- in $\cite{viola}$, Viola and Jones trained a 37 layer decision tree to achieve over 85 percent performance, using thousands of positive examples and millions of negative examples. Due to limitation of time and machines, we use a decision tree of roughly 10 layers. Once we crop out heads from the original images, we use boost algorithm to train a classifier to classify cat heads and dog heads. This classifier will be much more accurate than classifiers directly trained from the whole image. In this part, we use HOOGs as our feature vectors. By training 200 cat heads and 200 dog heads, we get a classifier with performance higher than $90\%$.

@@

\begin{thebibliography}{99}
\bibitem{viola} 
\bibitem{sun}
\bibitem{golle} 
\bibitem{asirra} J. Elson, J. Douceur, J. Howell and J. Saul. \textit{Asirra: a CAPTCHA that exploits interest-aligned manual image categorization.} In Proc. of ACM CCS 2007, pp. 366-374.
\end{thebibliography}
\end{document}
